### 2018-02-13 article.tex
init

\documentclass[twoside,twocolumn]{article}

\usepackage{blindtext} % Package to generate dummy text throughout this template

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[utf8]{inputenc}
\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
	\posttitle{\end{center}} % Article title closing formatting
\title{Article Title} % Article title
\author{%
	\textsc{ŁJohn Smith}\thanks{A thank you or further information} \\[1ex] % Your name
	\normalsize University of California \\ % Your institution
	\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
	%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
	%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
	%\normalsize University of Utah \\ % Second author's institution
	%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
	\begin{abstract}
		\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
	\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

	% Print the title
	\maketitle

	%----------------------------------------------------------------------------------------
	%	ARTICLE CONTENTS
	%----------------------------------------------------------------------------------------

	\section{Introduction}

	\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
	\blindtext % Dummy text

	\blindtext % Dummy text

	%------------------------------------------------

	\section{Methods}

	Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
	\begin{itemize}
		\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
		\item Curabitur feugiat
		\item turpis sed auctor facilisis
		\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
		\item Fusce fermentum, mi sit amet euismod rutrum
		\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
		\item Pellentesque bibendum pretium aliquet
	\end{itemize}
	\blindtext % Dummy text

	Text requiring further explanation\footnote{Example footnote}.

	%------------------------------------------------

	\section{Results}

	\begin{table}
		\caption{Example table}
		\centering
		\begin{tabular}{llr}
			\toprule
			\multicolumn{2}{c}{Name} \\
			\cmidrule(r){1-2}
			First name & Last Name & Grade \\
			\midrule
			John & Doe & $7.5$ \\
			Richard & Miles & $2$ \\
			\bottomrule
		\end{tabular}
	\end{table}

	\blindtext % Dummy text

	\begin{equation}
	\label{eq:emc}
	e = mc^2
	\end{equation}

	\blindtext % Dummy text

	%------------------------------------------------

	\section{Discussion}

	\subsection{Subsection One}

	A statement requiring citation \cite{Figueredo:2009dg}.
	\blindtext % Dummy text

	\subsection{Subsection Two}

	\blindtext % Dummy text

	%----------------------------------------------------------------------------------------
	%	REFERENCE LIST
	%----------------------------------------------------------------------------------------

	\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

		\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
		Figueredo, A.~J. and Wolf, P. S.~A. (2009).
		\newblock Assortative pairing and life history strategy - a cross-cultural
		study.
		\newblock {\em Human Nature}, 20:317--330.

	\end{thebibliography}

	%----------------------------------------------------------------------------------------

\end{document}
.

### 2018-02-14 article.tex
intro part

@@
 	\posttitle{\end{center}} % Article title closing formatting
-\title{Article Title} % Article title
+\title{Content-based recommendations in~e-commerce services} % Article title
 \author{%
-	\textsc{ŁJohn Smith}\thanks{A thank you or further information} \\[1ex] % Your name
-	\normalsize University of California \\ % Your institution
+	\textsc{John Smith}\thanks{A thank you or further information} \\[1ex] % Your name
+	\normalsize Warsaw University of Technology \\ % Your institution
+	\normalsize Faculty of Mathematics and Information Science \\
+	\normalsize ul. Koszykowa 75 \\
+	\normalsize 00-662 Warsaw, Poland \\
 	\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
@@
 	\begin{abstract}
-		\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
+		The subject of this paper focuses on issues of determining a semantic similarity between text
+		documents and recommendations of similar documents. A detailed problem comes from the online
+		auction site Allegro, which has a section of articles describing products available on the platform.
+		This section offers a recommendation system for similar textual articles based on their
+		content. The aim of this paper is to investigate a possibility of improving the existing recommendation
+		system using semantic text analysis methods.
+		In this paper, I adapt some state-of-the-art methods for determining a similarity between
+		text documents to the above problem, I introduce measures to evaluate a performance of these
+		methods and analyze possibilities of using them in the real system.
 	\end{abstract}
+	{\bf Keywords:} recommendations, natural language processing, word embedding, semantics, allegro
+
 }
@@
 
-	%----------------------------------------------------------------------------------------
-	%	ARTICLE CONTENTS
-	%----------------------------------------------------------------------------------------
+	\section{Introduction}
 
-	\section{Introduction}
+	Recommendation systems are often part of web services.
+
+	The key issue of recommendations generation is how suggested items are relevant to these which the user is interested in.
+
+	We can divide recommendation systems into two groups: collaborative and  content-based filtering.
+The first one assumes that user is likely to be interested in items which also users similar to s/he were interested in.
+In this paper we are focusing on the second group in which recommended items are similar to these that the user liked so far.
+
+	In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.
+
+	Allegro - the biggest marketplace platform in Eastern Europe contains a section presenting text articles concerning products available vie the platform.
+Currently there is a list of links to articles similar to given one.
+	% cel badania - sprawdzić czy można zastąpić używaną do tej pory metodę opartą o zapytanie elasticsearchowe
 
@@
 
-	\section{Results}
+	\section{Dataset}
+
+	Given dataset consists of 20000 textual articles concerning different products available via Allegro platform.
+
+	\section{Results and discussion}
+
+	% metody ewaluacji i wyniki
 
@@
 
-	\section{Discussion}
+	\section{Conclusion}
 
@@
 	\blindtext % Dummy text
-
-	%----------------------------------------------------------------------------------------
-	%	REFERENCE LIST
-	%----------------------------------------------------------------------------------------
 

### 2018-02-21 article.tex
most of introduction

@@
 
+\usepackage{graphicx}
+\graphicspath{ {img/} }
+
 %----------------------------------------------------------------------------------------
@@
 	\begin{abstract}
-		The subject of this paper focuses on issues of determining a semantic similarity between text
-		documents and recommendations of similar documents. A detailed problem comes from the online
-		auction site Allegro, which has a section of articles describing products available on the platform.
-		This section offers a recommendation system for similar textual articles based on their
-		content. The aim of this paper is to investigate a possibility of improving the existing recommendation
-		system using semantic text analysis methods.
-		In this paper, I adapt some state-of-the-art methods for determining a similarity between
-		text documents to the above problem, I introduce measures to evaluate a performance of these
-		methods and analyze possibilities of using them in the real system.
+			%TODO Pierwsze zdanie: zagajenie, że systemy reko są ważne
+		%TODO Dalej: In this paper..
+
+		Recommendation systems play an important role in modern e-commerce services.
+The more relevant items are presented to the user, the more likely s/he is to stay on a website and eventually make a transaction.
+In this paper, we adapt some state-of-the-art methods for determining similarities between text documents to content-based recommendations problem.
+The aim is to investigate a possibility of improving the existing recommendation system being a part of Allegro e-commerce platform using semantic text analysis methods.
+As a conclusion we show, that there is no significant difference between examined methods and previously used elasticsearch-based query in content-based recommendation task.
+
 	\end{abstract}
@@
 
-	Recommendation systems are often part of web services.
+	%TODO napisać, że to ważne
 
+	%TODO rozwiązaniem są systemy rekomendacji
+
+	%TODO dzielą się na dwa typy
+
+	% Po kolei wymienić metody: LSA, LDA, bengio, collobert, word2vec itp...
+	%Zagajenie
+	Recommendation systems are commonly used in e-commerce services. Such a system gives profit to both the user, allowing him to get to the information he is
+	he could not find, or know, that such information exists, as well as the owner website, which depends on attracting users to you they used his services to the greatest extent.
 	The key issue of recommendations generation is how suggested items are relevant to these which the user is interested in.
 
+	%Lekkie wprowadzenie do rekomendacji
 	We can divide recommendation systems into two groups: collaborative and content-based filtering.
@@
 
-	In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.
+	%O Allegro
+	A detailed problem comes from the on-line auction site Allegro.
+Allegro --- the biggest marketplace platform in Eastern Europe --- contains a section presenting text articles concerning products available via the platform.
+Currently there is a list of links to articles similar to given one.
+Using elasticsearch
 
-	Allegro - the biggest marketplace platform in Eastern Europe contains a section presenting text articles concerning products available vie the platform.
-Currently there is a list of links to articles similar to given one.
-	% cel badania - sprawdzić czy można zastąpić używaną do tej pory metodę opartą o zapytanie elasticsearchowe
+	%Synteza: co będziemy robić z rekomendacjami w Allegro
+	The subject of this paper focuses on issues of determining a semantic similarity between text
+	documents and recommendations of similar documents.
+In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.%TODO wymienić metody???
 
-	\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
-	\blindtext % Dummy text
+	%Plan artykułu
+	In the following sections we describe topics in detail...
+	%------------------------------------------------
 
-	\blindtext % Dummy text
+	\section{Dataset}
+	%TODO Skąd pochodzi zbiór danych
 
-	%------------------------------------------------
+	Given dataset consists of 20000 text articles describing several categories of products available via Allegro platform.
+Single record consists of article contents and metadata attached by an author of the article.
+
+	Id, category, keywords.
+
+	All articles are written in Polish. The vocabulary based on the articles set contains many industry-specific words like brands and models names, books titles and technical words.
+
+	Moreover raw articles contain some tags responsible for images and hyperlinks present on the website.
+
+	%TODO Preprocessing
 
@@
 
-	Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
-	\begin{itemize}
-		\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
-		\item Curabitur feugiat
-		\item turpis sed auctor facilisis
-		\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
-		\item Fusce fermentum, mi sit amet euismod rutrum
-		\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
-		\item Pellentesque bibendum pretium aliquet
-	\end{itemize}
-	\blindtext % Dummy text
+	\subsection{Preprocessing}
+
+	The following describes the next steps of the pre-processing of text that he performs on his own
+	collection of articles.
+	\begin{enumerate}
+		\item Cleansing the text from the redundant, previously mentioned markers. From the viewpoint of
+	semantic analysis of the text they are useless or harmful (they cause some
+	"Pollution" of the text). So I remove them using properly constructed ones
+	regular expressions. An example of such a tag is! [2\_new.jpg] (http: // (...)
+	'2\_new.jpg') placing the picture in the middle of the text (the content of the URL removed the reasons
+	confidentiality).
+		\item Removal of stopwords - usually short words that do not mean anything
+	the whole article. They are, for example, "in", "from", "because". Removing them reduces the number of words
+	document, thus shortening the processing time. As they say these words
+	often, removing them gives you the opportunity to emphasize the meaning of other words that have an impact
+	on the real meaning of the whole article. The collection of alloy words is derived from [31].
+		\item Bringing all the words of the document to lowercase letters. It helps to unify the character
+	parts of words with the same meaning, among which one occurs at the beginning of the sentence,
+	and others in the middle.
+		\item Breaking down the words connected with the thought. Experience at a later stage (tokenization)
+	shows that the tool making it (Morfologik [20]) does not deal with these types of words and leaves them in the unchanged grammatical form (eg "white and red"). So it is necessary
+	the manual execution of the mechanism by which I break such words into characters
+	compatible with the tokenizer. The earlier one was needed to perform the appropriate function
+	analysis of this type of words for the behavior of the two elements depending on them
+	the type, case and occurrence of specific letters in the suffixes of the component words. depended
+	me not to break down words that are my own names or symbols of devices.
+		\item Tokenization. This is the most important element of the whole process. It's about bringing words
+	with the same meaning, and different grammatical form to the same form. A big hurdle
+	here is the degree of complexity of the Polish language and the number of exceptions that this one has
+	language has. As an example, you can use the word "have", which one of the forms is "has",
+	the next is "have it". The goal of the stage is to bring each of these words to the basic form
+	"have". To carry out this operation, he uses the Morfologik tool [20].
+		\end{enumerate}
+
+	The above steps lead the data to a state in which you can apply semantic techniques
+	text analysis. The dictionary built on the pre-processed body contains 98174 unique
+	words, and 7409145 all words (with repetitions).
+
+	the overwhelming majority of the words of the dictionary built on the body are the words appearing
+	rarely.
+	\subsection{Model building}
+
+	Word2Vec authors offer pretrained model but only for English language. For Polish it's more difficult...
+	Lack of presumably important words like brand and model names etc.
 
@@
 
+	\subsection{Evaluation}
+
+	In order to compare the methods used to determine the similarity between the articles necessary
+	there is the formalization of certain measures of this similarity.
+
+	In practice, however, it is rarely worth the value of a given element of the ranking
+	is adequate to the query generating this ranking.
+
+	Evaluation of recommendations generation methods is a nontrivial task.
+A degree of similarity of two articles can be perceived differently by different persons.
+Therefore we decided to evaluate methods' performance with ....
+First with each tested method we choose 6 most similar articles for 50 randomly chosen base articles.
+Next we split them into pairs: base article --- similar article; it gave us $5*50=250$ pairs for a method.
+After that 5 persons individually evaluated a similarity of pairs of articles giving scores in scale 1-10.
+Finally we took an average score for each pair and it allowed us to calculate an average score for each method.
+Besides tested methods we evaluated also previous Allegro method and randomly generated pairs of articles just for a comparison purpose.
+
 	%------------------------------------------------
-
-	\section{Dataset}
-
-	Given dataset consists of 20000 textual articles concerning different products available via Allegro platform.
 
@@
 
-	\begin{table}
-		\caption{Example table}
-		\centering
-		\begin{tabular}{llr}
-			\toprule
-			\multicolumn{2}{c}{Name} \\
-			\cmidrule(r){1-2}
-			First name & Last Name & Grade \\
-			\midrule
-			John & Doe & $7.5$ \\
-			Richard & Miles & $2$ \\
-			\bottomrule
-		\end{tabular}
-	\end{table}
-
-	\blindtext % Dummy text
-
-	\begin{equation}
-	\label{eq:emc}
-	e = mc^2
-	\end{equation}
-
-	\blindtext % Dummy text
+	%\begin{table}
+	%	\caption{Example table}
+	%	\centering
+	%	\begin{tabular}{llr}
+	%		\toprule
+	%		\multicolumn{2}{c}{Name} \\
+	%		\cmidrule(r){1-2}
+	%		First name & Last Name & Grade \\
+	%		\midrule
+	%		John & Doe & $7.5$ \\
+	%		Richard & Miles & $2$ \\
+	%		\bottomrule
+	%	\end{tabular}
+	%\end{table}
 
@@
 
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.45\textwidth]{results.png}
+		\caption{}
+		%\label{fig:warstwy}
+	\end{figure}
+
+	Expert evaluation directly shows that none of the tested methods is significantly different
+	from others. None of the tested adaptations of the methods of semantic text analysis does not depart as well
+	from the current method used in Allegro. The difference between the best method (FastText)
+	and the worst (LDA) is around 9%. Each of the tested methods also gave a significant result
+	better than the random method.
+
+	To answer the question posed at the beginning of this work, i.e. whether the semantic method
+	Natural language analysis adapted to determine recommendations are in the state
+	to match the quality of the current method used in Allegro, he performs the test he has
+	to check whether there are grounds to believe that the results of any of the methods subjected
+	expert judgment is detached statistically significantly from the rest of the tested methods.
+	The statistical test that I carry out is the Kruskal-Wallis test. H0 accepts for the null hypothesis
+	he equality of distributions of distributions in the populations from which the samples originated.
+	In earlier tests, users assessed the similarity between the article and everyone
+	from articles recommended for it, determined by evaluated methods. For data
+	Kruskal-Wallis test entry accepts tests corresponding to test results for each
+	from methods (except for the random method) submitted from the average assessment of users for the most relevant
+	recommendations for each of the tested base articles.
+	In the test, the level of significance is assumed? = 0.05. Finally, as a result of the Kruskal test
+	Wallis receives p = 0.0571>? On the basis of which I state that there are no reasons to
+	reject the null hypothesis - the difference between the quality of the recommendations of the tested methods is not
+	56
+	5.5. Test summary
+	statistically significant. It means that neither of the tested semantic methods does not stick out
+	from others, neither the previous Allegro method is significantly better / worse than others
+	tested methods.
+
 	\section{Conclusion}
 
-	\subsection{Subsection One}
+	Comparison of the best configurations of the tested methods showed that there are no significant differences
+	between methods of semantic text analysis adapted to the task of generating recommendations
+	and the previous method used in Allegro based on the query for the Elasticsearch engine.
 
-	A statement requiring citation \cite{Figueredo:2009dg}.
-	\blindtext % Dummy text
+	After analyzing the test results
+	you can answer: yes, each of the methods of semantic analysis of the natural language in yours
+	the best configuration can be adapted to generate article recommendations
+	based on the content of the article currently displayed by the user of the website. recommendations
+	these in the opinion of users do not undermine the quality of the current method.
+	Using the methods of semantic text analysis allows to capture the hidden similarities between
+	documents, where the documents combine not the same words or synonyms, but some abstract ones
+	concepts related to each other. An important advantage of semantic methods compared to the previous one
+	the method used in Allegro is the fact that they are based only on content
+	articles. This frees the authors of the articles from independently providing them with additional metatags,
+	of which the current method is used to a large extent.
 
-	\subsection{Subsection Two}
-
-	\blindtext % Dummy text
-
-	\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
+	\begin{thebibliography}{99}
 
@@
 
+		\bibitem{allegro}
+		Opis Allegro
+		\url{https://magazyn.allegro.pl/3333-serwis-allegro-to-nasz-sposob-na-wasze-szybkie-i-wygodne-zakupy-przez-internet}
+		(dostęp 07.05.2017)
+
+		\bibitem{bengio}
+		Y. Bengio, R. Ducharme, P. Vincent, C. Jauvin,
+		\emph{A Neural Probabilistic Language Model},
+		Journal of Machine Learning Research 3 1137–1155,
+		2003
+
+		\bibitem{lda}
+		D. M. Blei, A. Y. Ng, M. I. Jordan,
+		\emph{Latent Dirichlet Allocation},
+		Journal of Machine Learning Research, tom 3 num. 4–5,
+		2003
+
+		\bibitem{aylien}
+		Blog Aylien
+		\url{http://blog.aylien.com/overview-word-embeddings-history-word2vec-cbow-glove/}
+		(dostęp 18.08.2017)
+
+		\bibitem{c_w}
+		R. Collobert, J. Weston,
+		\emph{A Unified Architecture for Natural Language Processing: Deep Neural Networks with Multitask Learning},
+		NEC Labs America,
+		2008
+
+		\bibitem{engines}
+		W. B. Croft, D. Metzler, T. Strohman,
+		\emph{Search Engines. Information Retrieval in Practice},
+		Pearson Education, Inc.,
+		6-9,
+		2015
+
+		\bibitem{lsa}
+		S. Deerwester, S. T. Dumais, G. W. Furnas, T. K. Landauer, R. Harshman,
+		\emph{Indexing by latent semantic analysis},
+		Journal of the American Society for Information Science, tom 41, num. 6,
+		1990
+
+		\bibitem{elastic}
+		Elasticsearch
+		\url{https://www.elastic.co/}
+		(dostęp 18.08.2017)
+
+		\bibitem{elastic_companies}
+		Firmy korzystające z Elasticsearch
+		\url{https://www.elastic.co/use-cases}
+		(dostęp 10.08.17)
+
+		\bibitem{firth}
+		J.R. Firth,
+		\emph{A synopsis of linguistic theory 1930-1955},
+		Oxford: Philological Society,
+		1957
+
+		\bibitem{svd}
+		G. H. Golub, W. Kahan,
+		\emph{Calculating the singular values and pseudo-inverse of a matrix},
+		Journal of the Society for Industrial and Applied Mathematics: Series B, Numerical Analysis. 2 (2),
+		1965
+
+		\bibitem{bow}
+		Z. S. Harris,
+		\emph{Distributional Structure},
+		Word,
+		10 (2/3): 146–62,
+		1954
+
+		\bibitem{google_word2vec}
+		Informacje o Word2vec
+		\url{https://code.google.com/archive/p/word2vec/}
+		(dostęp 26.05.2017)
+
+		\bibitem{ndcg}
+		K. Jarvelin, J. Kekalainen,
+		\emph{Cumulated gain-based evaluation of IR techniques},
+		University of Tampere,
+		2002
+
+		\bibitem{fasttext}
+		A. Joulin, E. Grave, P. Bojanowski T. Mikolov,
+		\emph{Bag of Tricks for Efficient Text Classification},
+		Facebook AI Research,
+		2016
+
+		\bibitem{pias}
+		P. Kędzia, G. Czachor, M. Piasecki, J. Kocoń
+		\emph{Vector representations of polish words (Word2Vec method)},
+		Wrocław University of Technology,
+		2016,
+		\url{https://clarin-pl.eu/dspace/handle/11321/327}
+		(dostęp 26.06.2017)
+
+		\bibitem{wmd}
+		M. J. Kusner, Y. Sun, N. I. Kolkin, K. Q. Weinberger,
+		\emph{From Word Embeddings To Document Distances},
+		International Conference on Machine Learning (ICML),
+		2015
+
+		\bibitem{lucene}
+		Lucene
+		\url{https://lucene.apache.org/}
+		(dostęp 18.08.2017)
+
+		\bibitem{word2vec}
+		T. Mikolov, K. Chen, G. Corrado, J. Dean,
+		\emph{Efficient Estimation of Word Representations in Vector Space},
+		International Conference on Machine Learning (ICML),
+		2013
+
+		\bibitem{morfologik}
+		Morfologik
+		\url{http://morfologik.blogspot.com/}
+		(dostęp 07.05.2017)
+
+		\bibitem{glove_cran}
+		Opis GloVe
+		\url{https://cran.r-project.org/web/packages/text2vec/vignettes/glove.html}
+		(dostęp 30.08.2017)
+
+		\bibitem{word2vec_tutorial}
+		Opis Word2vec
+		\url{http://mccormickml.com/2016/04/19/word2vec-tutorial-the-skip-gram-model/}
+		(dostęp 26.05.2017)
+
+		\bibitem{emd_method}
+		O. Pele, M. Werman,
+		\emph{Fast and robust earth mover's distances},
+		ICCV,
+		2009
+
+		\bibitem{glove}
+		J. Pennington, R. Socher, C. D. Manning,
+		\emph{GloVe: Global Vectors for Word Representation},
+		Computer Science Department, Stanford University, Stanford, CA 94305,
+		2014
+
+		\bibitem{all_naj}
+		Porównanie największych polskich serwisów aukcyjnych
+		\url{http://gadzetomania.pl/11824,zakupy-w-sieci-porownanie-najwiekszych-polskich-serwisow-aukcyjnych-2}
+		(dostęp 09.08.17)
+
+		\bibitem{handbook}
+		F. Ricci, L. Rokach, B. Shapira,
+		\emph{Introduction to Recommender Systems Handbook},
+		Springer,
+		1-4,
+		2011
+
+		\bibitem{handbook_col}
+		F. Ricci, L. Rokach, B. Shapira,
+		\emph{Introduction to Recommender Systems Handbook},
+		Springer,
+		145-147,
+		2011
+
+		\bibitem{handbook_cb}
+		F. Ricci, L. Rokach, B. Shapira,
+		\emph{Introduction to Recommender Systems Handbook},
+		Springer,
+		73-75,
+		2011
+
+		\bibitem{emd}
+		Y. Rubner, C. Tomasi, L. J. Guibas,
+		\emph{The Earth Mover's Distance as a Metric for Image Retrieval},
+		Computer Science Department, Stanford University,
+		1,
+		2000
+
+		\bibitem{tf_idf}
+		G. Salton and M. McGill,
+		\emph{Introduction to modern information retrieval},
+		McGraw-Hill,
+		1983
+
+		\bibitem{stopwords}
+		Słowa stopu w Wikipedii
+		\url{https://pl.wikipedia.org/wiki/Wikipedia:Stopwords}
+		(dostęp 15.04.2017)
+
+		\bibitem{slownik}
+		Słownik Języka Polskiego PWN
+		\url{http://sjp.pwn.pl/sjp/artykul;2441396.html}
+		(dostęp 07.05.2017)
+
+		\bibitem{screen_allegro}
+		Strona Allegro z artykułem
+		\url{https://allegro.pl/artykul/jaka-farba-dla-alergika-55917/}
+		(dostęp 26.06.2017)
+
+		\bibitem{wordnet}
+		Wordnet
+		\url{http://plwordnet.pwr.wroc.pl/wordnet/}
+		(dostęp 28.06.2017)
+
 	\end{thebibliography}

### 2018-02-22 article.tex
Refactor and conclusion

--- 2018-02-13 article.tex
@@
 	\begin{abstract}
-		\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
+			%TODO Pierwsze zdanie: zagajenie, że systemy reko są ważne
+		%TODO Dalej: In this paper..
+
+		Recommendation systems play an important role in modern e-commerce services.
+The more relevant items are presented to the user, the more likely s/he is to stay on a website and eventually make a transaction.
+In this paper, we adapt some state-of-the-art methods for determining similarities between text documents to content-based recommendations problem.
+The aim is to investigate a possibility of improving the existing recommendation system being a part of Allegro e-commerce platform using semantic text analysis methods.
+As a conclusion we show, that there is no significant difference between examined methods and previously used elasticsearch-based query in content-based recommendation task.
+
 	\end{abstract}
+	{\bf Keywords:} recommendations, natural language processing, word embedding, semantics, allegro
+
 }
@@
 	\maketitle
-
-	%----------------------------------------------------------------------------------------
-	%	ARTICLE CONTENTS
-	%----------------------------------------------------------------------------------------
-
+	%INTRODUCTION---------------------------------------------------------------------------------------------------------------------------------------
 	\section{Introduction}
 
-	\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
-	\blindtext % Dummy text
+	%TODO napisać, że to ważne
 
-	\blindtext % Dummy text
+	%TODO rozwiązaniem są systemy rekomendacji
 
-	%------------------------------------------------
+	%TODO dzielą się na dwa typy
 
+	% Po kolei wymienić metody: LSA, LDA, bengio, collobert, word2vec itp...
+	%Zagajenie
+	Recommendation systems are commonly used in e-commerce services. Such a system gives profit to both the user, allowing him to get to the information he is
+	he could not find, or know, that such information exists, as well as the owner website, which depends on attracting users to you they used his services to the greatest extent.
+	The key issue of recommendations generation is how suggested items are relevant to these which the user is interested in.
+
+	%Lekkie wprowadzenie do rekomendacji
+	We can divide recommendation systems into two groups: collaborative and content-based filtering.
+The first one assumes that user is likely to be interested in items which also users similar to s/he were interested in.
+In this paper we are focusing on the second group in which recommended items are similar to these that the user liked so far.
+
+	%O Allegro
+	A detailed problem comes from the on-line auction site Allegro.
+Allegro --- the biggest marketplace platform in Eastern Europe --- contains a section presenting text articles concerning products available via the platform.
+Currently there is a list of links to articles similar to given one.
+Using elasticsearch
+
+	%Synteza: co będziemy robić z rekomendacjami w Allegro
+	The subject of this paper focuses on issues of determining a semantic similarity between text
+	documents and recommendations of similar documents.
+In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.%TODO wymienić metody???
+
+	%Plan artykułu
+	In the following sections we describe topics in detail...
+	%DATASET------------------------------------------------------------------------------------------------------------------------------------
+	\section{Dataset}
+	%TODO Skąd pochodzi zbiór danych
+
+	As mentioned our dataset comes form Allegro e-commerce platform.
+It consists of 20000 text articles describing several categories of products available via Allegro platform.
+Single record consists of article contents and metadata attached by an author of the article.
+As significant metadata we consider ,,category'' and ,,keywords''.
+
+	%krótko opisać keywords i category
+
+	All articles are written in Polish.
+The vocabulary based on the articles set contains many industry-specific words like brands and models names, books titles and technical words.
+Moreover raw articles contain some tags responsible for images and hyperlinks present on the website.
+
+	A standard activity before building a model is preprocessing of a row dataset. The following enumeration describes steps of the preprocessing that we performed.
+	collection of articles.
+	\begin{enumerate}
+
+		\item Cleansing the text from the redundant, previously mentioned tags. From the viewpoint of semantic analysis they are useless or even noxious. So I remove them using properly constructed ones
+		regular expressions.
+An example of such a tag is \texttt{[2\_new.jpg] (http: // (...)'2\_new.jpg')} placing the picture in the middle of the text (the content of the URL removed due to confidentiality reasons).
+
+		\item Removal of stopwords - usually short words carrying very little information about the actual document contents, e.g.
+,,in'', ,,from'', ,,because'' etc.
+Removing them reduces the number of words in a document and the processing time therein.
+Full list of stopwords comes from [31].
+
+		\item Converting all the words of the document to lowercase letters. It helps to unify words with the same meaning, but written using both uppercase and lowercase letters.
+
+		\item Breaking down the words connected with the hyphen.
+Experience at a later lemmatisation stage shows that the tool used to it (Morfologik [20]) does not cope with these types of words and leaves them in the unchanged grammatical form.
+This made it necessary to build our own tool that breaks such words into sub-words compatible with the lemmatiser.
+
+		\item Tokenization and lemmatisation.
+This is the most important element of the process.
+It's about separating text into individual words and converting the words with the same meaning, and different grammatical form to the same form.
+Complexity of the Polish language and the number of exceptions that this language has are making this problem harder than in many other languages.
+To carry out this operation, we used the Morfologik tool [20].
+
+	\end{enumerate}
+
+	The above steps lead the data to a state in which you can apply semantic techniques
+	text analysis. The dictionary built on the pre-processed body contains 98174 unique
+	words, and 7409145 all words (with repetitions).
+
+	the overwhelming majority of the words of the dictionary built on the body are the words appearing
+	rarely.
+	%METHODS-------------------------------------------------------------------------------------------------------------------------------------
 	\section{Methods}
 
-	Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
-	\begin{itemize}
-		\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
-		\item Curabitur feugiat
-		\item turpis sed auctor facilisis
-		\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
-		\item Fusce fermentum, mi sit amet euismod rutrum
-		\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
-		\item Pellentesque bibendum pretium aliquet
-	\end{itemize}
-	\blindtext % Dummy text
+	Emerging popularity of word embeddings methods started
+
+	Next we had to choose an evaluation method....
+
+	\subsection{Model building}
+
+	Below enumeration contains text analysis methods we decided to adapt for our content-based recommendations task.
+
+	\begin{enumerate}
+		\item Latent semantic analysis
+		\item Latent Dirichlet allocation
+		\item Word2Vec %We decided to train word embedding models on our dataset.
+		\item GloVe
+		\item FastText
+	\end{enumerate}
+
+	Word2Vec authors offer pretrained model but only for English language. For Polish it's more difficult...
+	Lack of presumably important words like brand and model names etc.
+
+	%Wzmianka o usrednianiu wektorów word embeddings
 
@@
 
-	%------------------------------------------------
+	\subsection{Evaluation}
 
-	\section{Results}
+	In order to compare the methods used to determine the similarity between the articles necessary
+	there is the formalization of certain measures of this similarity.
 
-	\begin{table}
-		\caption{Example table}
+	In practice, however, it is rarely worth the value of a given element of the ranking
+	is adequate to the query generating this ranking.
+
+	Evaluation of recommendations generation methods is a nontrivial task.
+A degree of similarity of two articles can be perceived differently by different persons.
+Therefore we decided to evaluate methods' performance with ....
+First with each tested method we choose 6 most similar articles for 50 randomly chosen base articles.
+Next we split them into pairs: base article --- similar article; it gave us $5*50=250$ pairs for a method.
+After that 5 persons individually evaluated a similarity of pairs of articles giving scores in scale 1-10.
+Finally we took an average score for each pair and it allowed us to calculate an average score for each method.
+Besides tested methods we evaluated also previous Allegro method and randomly generated pairs of articles just for a comparison purpose.
+
+	%RESULTS & DISCUSSION-----------------------------------------------------------------------------------------------------------------------------------------------------------
+	\section{Results and discussion}
+	In order to compare aforementioned methods we performed described expert evaluation.
+The evaluated methods were: LSA, LDA, word2vec, GloVe, FastText, previous Allegro elasticsearch-based method and randomly chosen pairs of articles.
+
+	Hyperparameters of the methods...
+
+	\begin{figure}
 		\centering
-		\begin{tabular}{llr}
-			\toprule
-			\multicolumn{2}{c}{Name} \\
-			\cmidrule(r){1-2}
-			First name & Last Name & Grade \\
-			\midrule
-			John & Doe & $7.5$ \\
-			Richard & Miles & $2$ \\
-			\bottomrule
-		\end{tabular}
-	\end{table}
+		\includegraphics[width=0.45\textwidth]{results.png}
+		\caption{}
+		%\label{fig:warstwy}
+	\end{figure}
 
-	\blindtext % Dummy text
+	Expert evaluation suggests that none of the tested methods is significantly different from others.
+The difference between the best method (FastText) and the worst one (LDA) is around 9\%.
+Each of the tested methods also gave a significantly better result than the random method.
 
-	\begin{equation}
-	\label{eq:emc}
-	e = mc^2
-	\end{equation}
+	To answer the question posed at the beginning of this work, i.e.
+whether the examined text analysis methods adapted to content-based recommendation task are able to match current method used in Allegro, we perform a test that's goal is to check whether there are grounds to believe that the results of any of the methods is statistically significantly different from the rest of the examined methods.
 
-	\blindtext % Dummy text
+	The statistical test that we carry out is the Kruskal-Wallis test. The null hypothesis $H_0$ assumes the equality of distributions in the populations from which the samples originated.
+	%do poprawienia---------------------------------------
+	In earlier tests, users assessed the similarity between the article and everyone from articles recommended for it, determined by evaluated methods.
 
-	%------------------------------------------------
+	For data Kruskal-Wallis test entry accepts tests corresponding to test results for each from methods (except for the random method) submitted from the average assessment of users for the most relevant recommendations for each of the tested base articles.
+	%-----------------------------------------------------
+	In the test, the level of significance is $\alpha = 0.05$.
+Finally, as the result of the Kruskal-Wallis test we received $p = 0.0571>\alpha$, on the basis of which we state that there are no reasons to	reject the null hypothesis --- the difference between the quality of the recommendations of the tested methods is not statistically significant.
+It means that neither of the tested semantic methods does not stick out from others, nor the previous Allegro method is significantly better/worse than other tested methods.
 
-	\section{Discussion}
+	%CONCLUSION--------------------------------------------------------------------------------------------------------------------------------------------------------------------
+	\section{Conclusion}
 
-	\subsection{Subsection One}
+	After analyzing the test results we can answer: yes, each of the examined methods of natural language semantic analysis in their best configuration can be adapted to generate article content-based recommendations.
+This means we can replace previously used method with e.g.
+FastText and any user should not feel any difference in recommendations quality.
 
-	A statement requiring citation \cite{Figueredo:2009dg}.
-	\blindtext % Dummy text
+	Using methods of semantic text analysis allows to capture the hidden similarities between documents, where the documents combine not the same words or synonyms, but some abstract concepts related to each other.
+An important advantage of semantic methods compared to the previous one is the fact that they are based only on article contents.
+This frees the authors of the articles from providing additional metadata, which the previous method uses in large extent.
 
-	\subsection{Subsection Two}
+	\begin{thebibliography}{99}
+		\bibitem{lda}
+		D. M. Blei, A. Y. Ng, M. I. Jordan,
+		\emph{Latent Dirichlet Allocation},
+		Journal of Machine Learning Research, tom 3 num. 4–5,
+		2003
 
-	\blindtext % Dummy text
+		\bibitem{lsa}
+		S. Deerwester, S. T. Dumais, G. W. Furnas, T. K. Landauer, R. Harshman,
+		\emph{Indexing by latent semantic analysis},
+		Journal of the American Society for Information Science, tom 41, num. 6,
+		1990
 
-	%----------------------------------------------------------------------------------------
-	%	REFERENCE LIST
-	%----------------------------------------------------------------------------------------
+		\bibitem{fasttext}
+		A. Joulin, E. Grave, P. Bojanowski T. Mikolov,
+		\emph{Bag of Tricks for Efficient Text Classification},
+		Facebook AI Research,
+		2016
 
-	\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
+		\bibitem{wmd}
+		M. J. Kusner, Y. Sun, N. I. Kolkin, K. Q. Weinberger,
+		\emph{From Word Embeddings To Document Distances},
+		International Conference on Machine Learning (ICML),
+		2015
 
-		\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
-		Figueredo, A.~J. and Wolf, P. S.~A. (2009).
-		\newblock Assortative pairing and life history strategy - a cross-cultural
-		study.
-		\newblock {\em Human Nature}, 20:317--330.
+		\bibitem{word2vec}
+		T. Mikolov, K. Chen, G. Corrado, J. Dean,
+		\emph{Efficient Estimation of Word Representations in Vector Space},
+		International Conference on Machine Learning (ICML),
+		2013
+
+		\bibitem{morfologik}
+		Morfologik
+		\url{http://morfologik.blogspot.com/}
+		(dostęp 07.05.2017)
+
+		\bibitem{glove}
+		J. Pennington, R. Socher, C. D. Manning,
+		\emph{GloVe: Global Vectors for Word Representation},
+		Computer Science Department, Stanford University, Stanford, CA 94305,
+		2014
 

### 2018-02-23 article.tex
Całe intro

@@
 In this paper, we adapt some state-of-the-art methods for determining similarities between text documents to content-based recommendations problem.
-The aim is to investigate a possibility of improving the existing recommendation system being a part of Allegro e-commerce platform using semantic text analysis methods.
+The goal is to investigate a possibility of improving an existing recommendation system being a part of Allegro e-commerce platform using semantic text analysis methods.
 As a conclusion we show, that there is no significant difference between examined methods and previously used elasticsearch-based query in content-based recommendation task.
@@
 \begin{document}
-
-	% Print the title
 	\maketitle
@@
 
-	%TODO napisać, że to ważne
-
-	%TODO rozwiązaniem są systemy rekomendacji
-
-	%TODO dzielą się na dwa typy
-
 	% Po kolei wymienić metody: LSA, LDA, bengio, collobert, word2vec itp...
 	%Zagajenie
-	Recommendation systems are commonly used in e-commerce services. Such a system gives profit to both the user, allowing him to get to the information he is
-	he could not find, or know, that such information exists, as well as the owner website, which depends on attracting users to you they used his services to the greatest extent.
+	Recommendation systems are commonly used in e-commerce services.
+Such system give profit to both a user as well as a website owner.
+They allow the user to get to an information s/he could not find, or even know, that such information exists.
+They also attract users to a service making them more likely to buy something, increasing website company's profit thereby.
 The key issue of recommendations generation is how suggested items are relevant to these which the user is interested in.
@@
 	%Lekkie wprowadzenie do rekomendacji
-	We can divide recommendation systems into two groups: collaborative and content-based filtering.
+	Generally we can divide recommendation systems into two groups: collaborative and content-based filtering.
 The first one assumes that user is likely to be interested in items which also users similar to s/he were interested in.
@@
 Allegro --- the biggest marketplace platform in Eastern Europe --- contains a section presenting text articles concerning products available via the platform.
-Currently there is a list of links to articles similar to given one.
-Using elasticsearch
+Next to article currently displayed by a user, there is a list of links to articles similar to given one.
+Previous recommendations determining mechanism is based on elasticsearch query and uses both an article text and some metadata attached to the article.
 
 	%Synteza: co będziemy robić z rekomendacjami w Allegro
-	The subject of this paper focuses on issues of determining a semantic similarity between text
-	documents and recommendations of similar documents.
-In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.%TODO wymienić metody???
+	In this paper we strive to check if some semantic text analysis methods, including newly proposed word embeddings, are able to replace previously used Allegro method.
+Examined methods are topic modeling methods: latent semantic analysis~\cite{lsa}, latent Dirichlet allocation~\cite{lda} and word embeddings methods: word2vec~\cite{word2vec}, fastText~\cite{fasttext} and GloVe~\cite{glove}.
 
 	%Plan artykułu
-	In the following sections we describe topics in detail...
+	In section 2 we make an analysis of the articles dataset and also we describe data preprocessing we performed.
+Section 3 is about methods used for building the model and next evaluate results.
+In section 4 we present the results and try to interpret them.
+The last section concludes the papers and proposes a direction of future work.
 	%DATASET------------------------------------------------------------------------------------------------------------------------------------
@@
 
-	The statistical test that we carry out is the Kruskal-Wallis test. The null hypothesis $H_0$ assumes the equality of distributions in the populations from which the samples originated.
+	The statistical test that we carry out is the Kruskal-Wallis test. In the test the null hypothesis $H_0$ assumes an equality of distributions in populations from which samples originated.
 	%do poprawienia---------------------------------------

### 2018-02-23 article.tex
Wszystko prócz 'methods'

@@
 
-	A standard activity before building a model is preprocessing of a row dataset. The following enumeration describes steps of the preprocessing that we performed.
-	collection of articles.
+	A standard activity before building a model is preprocessing of a raw dataset. The following enumeration describes steps of the preprocessing that we performed.
 	\begin{enumerate}
 
-		\item Cleansing the text from the redundant, previously mentioned tags. From the viewpoint of semantic analysis they are useless or even noxious. So I remove them using properly constructed ones
-		regular expressions.
+		\item Cleansing the text from the redundant, previously mentioned tags.
+From the viewpoint of semantic analysis they are useless or even noxious.
+That is why we remove them using properly constructed regular expressions.
 An example of such a tag is \texttt{[2\_new.jpg] (http: // (...)'2\_new.jpg')} placing the picture in the middle of the text (the content of the URL removed due to confidentiality reasons).
 
-		\item Removal of stopwords - usually short words carrying very little information about the actual document contents, e.g.
+		\item Removal of stopwords --- usually short words carrying very little information about the actual document contents, e.g.
 ,,in'', ,,from'', ,,because'' etc.
-Removing them reduces the number of words in a document and the processing time therein.
-Full list of stopwords comes from [31].
+Removing them reduces the number of words in a document and the processing time thereby.
 
-		\item Converting all the words of the document to lowercase letters. It helps to unify words with the same meaning, but written using both uppercase and lowercase letters.
+		\item Converting all words of a document to lowercase letters. It helps to unify words with the same meaning, but written using both uppercase and lowercase letters.
 
-		\item Breaking down the words connected with the hyphen.
-Experience at a later lemmatisation stage shows that the tool used to it (Morfologik [20]) does not cope with these types of words and leaves them in the unchanged grammatical form.
+		\item Breaking down the words connected with a hyphen.
+Experience at a later lemmatisation stage shows that the tool used to it (Morfologik~\cite{morfologik}) does not cope with these types of words and leaves them in the unchanged grammatical form.
 This made it necessary to build our own tool that breaks such words into sub-words compatible with the lemmatiser.
@@
 Complexity of the Polish language and the number of exceptions that this language has are making this problem harder than in many other languages.
-To carry out this operation, we used the Morfologik tool [20].
+To carry out this operation, we used the Morfologik tool~\cite{morfologik}.
 
@@
 
-	The above steps lead the data to a state in which you can apply semantic techniques
-	text analysis. The dictionary built on the pre-processed body contains 98174 unique
-	words, and 7409145 all words (with repetitions).
-
-	the overwhelming majority of the words of the dictionary built on the body are the words appearing
-	rarely.
+	The above steps lead the data to a state in which we can apply examined semantic techniques of text analysis.
+The dictionary built on the preprocessed corpus contains 98174 unique	words and 7409145 all words (with repetitions).	The overwhelming majority of the words of the dictionary built on the body are the words appearing rarely.
 	%METHODS-------------------------------------------------------------------------------------------------------------------------------------
@@
 
+	Hyperparameters of the methods...
+
 	Word2Vec authors offer pretrained model but only for English language. For Polish it's more difficult...
@@
 
-	In order to compare the methods used to determine the similarity between the articles necessary
-	there is the formalization of certain measures of this similarity.
+	In order to compare the methods used to determine the similarity between the articles, the formalization of certain measures of this similarity seems necessary.
 
@@
 
-	Hyperparameters of the methods...
-
 	\begin{figure}
@@
 	To answer the question posed at the beginning of this work, i.e.
-whether the examined text analysis methods adapted to content-based recommendation task are able to match current method used in Allegro, we perform a test that's goal is to check whether there are grounds to believe that the results of any of the methods is statistically significantly different from the rest of the examined methods.
+whether the examined text analysis methods adapted to content-based recommendation task are able to match the previous method used in Allegro, we perform a test that's goal is to check whether there are grounds to believe that the results of any of the methods is statistically significantly different from the rest of the examined methods.
 
-	The statistical test that we carry out is the Kruskal-Wallis test. In the test the null hypothesis $H_0$ assumes an equality of distributions in populations from which samples originated.
-	%do poprawienia---------------------------------------
-	In earlier tests, users assessed the similarity between the article and everyone from articles recommended for it, determined by evaluated methods.
+	The statistical test that we carry out is the Kruskal-Wallis test.
+In the test the null hypothesis $H_0$ assumes an equality of distributions in populations from which samples originated.	As input data the Kruskal-Wallis test takes samples corresponding to expert evaluation of each method consisting of an average score made by users for the most relevant recommendation for each of the examined base articles.
 
-	For data Kruskal-Wallis test entry accepts tests corresponding to test results for each from methods (except for the random method) submitted from the average assessment of users for the most relevant recommendations for each of the tested base articles.
-	%-----------------------------------------------------
 	In the test, the level of significance is $\alpha = 0.05$.
-Finally, as the result of the Kruskal-Wallis test we received $p = 0.0571>\alpha$, on the basis of which we state that there are no reasons to	reject the null hypothesis --- the difference between the quality of the recommendations of the tested methods is not statistically significant.
-It means that neither of the tested semantic methods does not stick out from others, nor the previous Allegro method is significantly better/worse than other tested methods.
+Finally, as the result of the Kruskal-Wallis test we received $p = 0.0571>\alpha$, on the basis of which we state that there are no reasons to reject the null hypothesis --- the quality difference between of recommendations generated by the tested methods is not statistically significant.
+It means that neither of the tested semantic methods sticks out from others, nor the previous Allegro method is significantly better/worse than other tested methods.
 

### 2018-02-23 article.tex
Wszystko wstępni

@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
+\fancyhead[C]{Content-based recommendations in~e-commerce service $\bullet$ February 2018} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 	\posttitle{\end{center}} % Article title closing formatting
-\title{Content-based recommendations in~e-commerce services} % Article title
+\title{Content-based recommendations in~e-commerce service} % Article title
 \author{%
-	\textsc{John Smith}\thanks{A thank you or further information} \\[1ex] % Your name
+	\textsc{AUTHOR}\\[1ex]%\thanks{A thank you or further information} \\[1ex] % Your name
 	\normalsize Warsaw University of Technology \\ % Your institution
@@
 	\normalsize 00-662 Warsaw, Poland \\
-	\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
+	\normalsize \href{mailto:mail}{mail} % Your email address
 	%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
@@
 	\begin{abstract}
-			%TODO Pierwsze zdanie: zagajenie, że systemy reko są ważne
-		%TODO Dalej: In this paper..
 
@@
 	\section{Methods}
-
-	Emerging popularity of word embeddings methods started
-
-	Next we had to choose an evaluation method....
+	%zagajenie------------------------------------------------------
+	Sudden increase of popularity of word embeddings methods started with introducing word2vec by Mikolov et al.
+in 2013\cite{word2vec}.
+This method converts words to vectors using a shallow neural network.
+Word2vec outperforms earlier approaches in terms of time complexity.
 
@@
 
+	Hyperparameters of examined methods were chosen based on preliminary automatic evaluation.
+For this purpose we took advantage of articles' metadata --- the more common categories/keywords two articles have, the more similar they are.
+Hyperparameters values, with which a method achieved the best score were for further evaluation described in next subsection.
+
 	Below enumeration contains text analysis methods we decided to adapt for our content-based recommendations task.
-
+	%metody i wartosci hiperparametrów
 	\begin{enumerate}
-		\item Latent semantic analysis
-		\item Latent Dirichlet allocation
-		\item Word2Vec %We decided to train word embedding models on our dataset.
-		\item GloVe
-		\item FastText
+		\item Latent semantic indexing~\cite{lsa} with 500 topics, labeled (\emph{lsi500})
+		\item Latent Dirichlet allocation~\cite{lda} with 900 topics, labeled (\emph{lda900})
+		\item Word2Vec~\cite{word2vec} with 300 length vectors, (labeled \emph{w2v300})  %We decided to train word embedding models on our dataset.
+			Word2Vec authors offer a pretrained model but only for English language.
+There exist pretrained models for Polish language (\cite{pias}).
+However due to possible lack of presumably important words like brand and model names etc.
+we decided to train a model independently using our entire articles corpus.
+Following methods: FastText and GloVe were examined with similar preparation.
+			%Wzmianka o usrednianiu wektorów word embeddings i wmd
+		\item FastText~\cite{fasttext} with 1000 length vectors, (labeled \emph{ft1000})
+		\item GloVe~\cite{glove} with 1000 length vectors, (labeled \emph{gv1000})
 	\end{enumerate}
 
-	Hyperparameters of the methods...
-
-	Word2Vec authors offer pretrained model but only for English language. For Polish it's more difficult...
-	Lack of presumably important words like brand and model names etc.
-
-	%Wzmianka o usrednianiu wektorów word embeddings
-
-	Text requiring further explanation\footnote{Example footnote}.
+	%Text requiring further explanation\footnote{Example footnote}.
 
@@
 
-	In order to compare the methods used to determine the similarity between the articles, the formalization of certain measures of this similarity seems necessary.
-
-	In practice, however, it is rarely worth the value of a given element of the ranking
-	is adequate to the query generating this ranking.
-
+	In order to compare the results of the methods used to determine a similarity between articles, a formalization of certain measures of this similarity was necessary.
 Evaluation of recommendations generation methods is a nontrivial task.
 A degree of similarity of two articles can be perceived differently by different persons.
-Therefore we decided to evaluate methods' performance with ....
-First with each tested method we choose 6 most similar articles for 50 randomly chosen base articles.
+Therefore we decided to evaluate methods' performance with help of real users, whose task was to asses similarity between articles pairs.
+
+	First with each tested method we choose 5 most similar articles for 50 randomly chosen base articles.
 Next we split them into pairs: base article --- similar article; it gave us $5*50=250$ pairs for a method.
@@
 	In order to compare aforementioned methods we performed described expert evaluation.
-The evaluated methods were: LSA, LDA, word2vec, GloVe, FastText, previous Allegro elasticsearch-based method and randomly chosen pairs of articles.
+The evaluated methods were: LSI, LDA, word2vec, GloVe, FastText, previous Allegro elasticsearch-based method and randomly chosen pairs of articles.
 
@@
 		\includegraphics[width=0.45\textwidth]{results.png}
-		\caption{}
+		\caption{Comparison of expert-evaluated methods results.}
 		%\label{fig:warstwy}
@@
 		\url{http://morfologik.blogspot.com/}
-		(dostęp 07.05.2017)
 
@@
 
+		\bibitem{pias}
+		P. Kędzia, G. Czachor, M. Piasecki, J. Kocoń
+		\emph{Vector representations of polish words (Word2Vec method)},
+		Wrocław University of Technology,
+		2016,
+		\url{https://clarin-pl.eu/dspace/handle/11321/327}
 	\end{thebibliography}

### 2018-02-23 article.tex
poprawki

@@
 Such system give profit to both a user as well as a website owner.
-They allow the user to get to an information s/he could not find, or even know, that such information exists.
+It allows the user to get to an information s/he could not find, or even know, that such information exists.
 They also attract users to a service making them more likely to buy something, increasing website company's profit thereby.
@@
 In section 4 we present the results and try to interpret them.
-The last section concludes the papers and proposes a direction of future work.
+The last section concludes the paper and proposes a direction of future work.
 	%DATASET------------------------------------------------------------------------------------------------------------------------------------
@@
 		\item Breaking down the words connected with a hyphen.
-Experience at a later lemmatisation stage shows that the tool used to it (Morfologik~\cite{morfologik}) does not cope with these types of words and leaves them in the unchanged grammatical form.
+Experience at a later lemmatisation stage shows that the tool used for this purpose (Morfologik~\cite{morfologik}) does not cope with these types of words and leaves them in the unchanged grammatical form.
 This made it necessary to build our own tool that breaks such words into sub-words compatible with the lemmatiser.
@@
 	Hyperparameters of examined methods were chosen based on preliminary automatic evaluation.
-For this purpose we took advantage of articles' metadata --- the more common categories/keywords two articles have, the more similar they are.
+For this purpose we took advantage of articles' metadata --- we assumed that the more common categories/keywords two articles had, the more similar they were.
 Hyperparameters values, with which a method achieved the best score were for further evaluation described in next subsection.
@@
 	\end{enumerate}
+
+	Word embeddings methods only converts words to vectors.
+In order to compare whole documents we needed to represent documents as vectors.
+For this purpose we examined two approaches.
+First one was a simple calculation of an average of vectors being representation of words included in an article.
+The second one was Word Mover's Distance\cite{wmd}.
+Unfortunately WMD turned out to be too slow to be used in production system.
 
